%-------------------------
% Resume in Latex
% Author : Jake Gutierrez
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
%   \textbf{\href{http://sourabhbajaj.com/}{\Large Sourabh Bajaj}} & Email : \href{mailto:sourabh@sourabhbajaj.com}{sourabh@sourabhbajaj.com}\\
%   \href{http://sourabhbajaj.com/}{http://www.sourabhbajaj.com} & Mobile : +1-123-456-7890 \\
% \end{tabular*}

\begin{center}
    \textbf{\Huge \scshape Harsh Vardhan Singh Chauhan} \\ \vspace{1pt}
    \small +91-9953944291 $|$ \href{https://medium.com/@harshtherocking}{\underline{medium.com/@harshtherocking}} $|$ 
    \href{https://linkedin.com/in/harshvschauhan/}{\underline{linkedin.com/in/harshvschauhan}} $|$
    \href{https://github.com/Harshtherocking}{\underline{https://github.com/Harshtherocking}}
\end{center}


%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Data Miner}{Dec. 2023 -- Jan 2024}
      {ScimerTech}{Remote}
      \resumeItemListStart
        \resumeItem{Scraped data from the \textbf{NIST} web-book, enhancing traditional data collection efficiency by \textbf{85\%} through \textbf{automated extraction} and \textbf{parsing} techniques.}
        \resumeItem{Conducted \textbf{spectroscopic analysis} to identify chemical compounds and functional groups in food samples, improving identification accuracy by \textbf{20\%}.}
        \resumeItem{Implemented \textbf{noise reduction} and \textbf{smoothing algorithms} for spectral data pre-processing, boosting data quality and accuracy by up to \textbf{79\%}. Utilized \textbf{1-D Convolution} and \textbf{Random Forest algorithms} for feature extraction, further increasing precision in spectroscopic analysis.}
      \resumeItemListEnd
      
% -----------Multiple Positions Heading-----------
   % \resumeSubSubheading
   %  {Software Engineer I}{Oct 2014 - Sep 2016}
   %  \resumeItemListStart
   %     \resumeItem{Apache Beam}
   %       {Apache Beam is a unified model for defining both batch and streaming data-parallel processing pipelines}
   %  \resumeItemListEnd
   % \resumeSubHeadingListEnd
%-------------------------------------------

    % \resumeSubheading
    %   {Data Science Intern}{July. 2023 -- Aug, 2023}
    %   {Oasis Infobyte}{Remote}
    %   \resumeItemListStart
    %     \resumeItem{Prediction model optimization for Car Price Regression models and Spam Email Classification along with Unemployment Analysis using \textbf{Principal component analysis} \& \textbf{Feature extraction}.}
    %     \resumeItem{\textbf{GUI implementation} for enhancing user consuming experience and seamless interaction with the software}
    % \resumeItemListEnd

  \resumeSubHeadingListEnd


%-----------PROJECTS-----------
\section{Projects}
    \resumeSubHeadingListStart
          
      \resumeProjectHeading
          {\textbf{Dependency-Aware Sentiment Analysis with GNN} $|$ \emph{Btech Paper}}{May 2024 -- Present}
          \resumeItemListStart
            \resumeItem{Built graph-based sentiment analysis model using \textbf{word} and \textbf{dependency embeddings}, and a custom \textbf{Message Passing} algorithm in GNN for \textbf{node-edge interaction}.}
            \resumeItem{Applied \textbf{graph embeddings} to model syntactic and semantic dependencies for enhanced \textbf{sentiment detection} and \textbf{learning dependency embeddings}.}
            % \resumeItem{}
          \resumeItemListEnd

    \resumeProjectHeading
          {\textbf{Nyaya (Justice) Chatbot} $|$ \emph{Department of Justice, India}}{Aug 2024 - Sept 2024}
          \resumeItemListStart
            \resumeItem{Set up and managed \textbf{Weaviate} \textbf{vector database} in \textbf{Docker} for scalable vector-based storage and retrieval.}
            \resumeItem{Improved \textbf{vector search} performance using the \textbf{Hierarchical Navigable Small World} (HNSW) algorithm.}
            \resumeItem{Built pipelines to preprocess and \textbf{ingest} data from various \textbf{file formats} including images, PDFs, and HTML.}
            \resumeItem{Applied \textbf{recursive retrieval} techniques to boost query efficiency and accuracy. Developed \textbf{prompts} for concise, \textbf{procedural responses} to enhance website navigation.}
          \resumeItemListEnd
          
        \resumeProjectHeading
          {\textbf{IIRS Spectral Classification of Lunar Surface} $|$ \emph{Bhartiya Antariksh Hackathon, ISRO}}{July 2024 -- Aug 2024}
          \resumeItemListStart
            \resumeItem{Utilized \textbf{MATLAB} to visualize and analyze \textbf{IIRS hyperspectral images}, enhancing the capability for detailed lunar geological analysis by providing clear, actionable insights from complex data sets.}
            \resumeItem{Applied \textbf{wavelet transformation} for advanced noise reduction, substantially improving the interpretability and quality of hyperspectral data and enabling more accurate analysis and assessment.}
            \resumeItem{Designed spectral classification models using \textbf{KNN} and \textbf{Gaussian clustering} attaining \textbf{82`\% accuracy} with successful GUI implementation via \textbf{MATLAB App Designer}.}
          \resumeItemListEnd
          
      \resumeProjectHeading
          {\textbf{Vue - Video Streaming Platform}}{Oct. 2023 -- Nov. 2023}
          \resumeItemListStart
            \resumeItem{Developed an \textbf{anime streaming platform} with a front-end, \textbf{user login system}, \textbf{live hosting rooms}, and interactive \textbf{comment features}} 
            \resumeItem{Applied \textbf{TorchVision} for profile picture pre-processing and \textbf{OpenCV} for \textbf{face detection} and \textbf{background removal}, effectively isolating and enhancing facial features.}
            \resumeItem{Implemented a \textbf{Hugging Face} pre-trained model to generate \textbf{custom cartoon avatars} from profile images, enhancing user personalization.}
          \resumeItemListEnd
    \resumeSubHeadingListEnd



%
%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: Python, C/C++, SQL, Java, Javascript, HTML, CSS, PHP, Latex, Bash, Markdown} \\
     \textbf{Frameworks}{: FastAPI, Pytorch, TensorFLow, PyGeometric, Hugging-Face, LangChain, LlamaIndex, StreamLit} \\
     \textbf{Developer Tools}{: Git, Docker, MongoDB, MLFlow, MATLAB, Envi, ImageJ} \\
     \textbf{Libraries}{: Pandas, NumPy, Matplotlib, Keras, SciPy, NLTK, Seaborn, OpenCV, Scikit-Learn, Spacy, NetworkX, beautifulSoup, Scrapy, OpenNLP, Graph4NLP, Fasttext, Transformer, Accelerate, PEFT, Milvus, DSPy}
    }}
 \end{itemize}


%-----------ACHIEVEMENT-------------------
\section{ACHIEVEMENT}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Bhartiya Antariksh Hackathon ISRO}{NRSC Hyderabad, India}
      {\textbf{1st Runner-up} : IIRS Spectral Image Classification for the Lunar Surface using AI/ML}{Aug 2024}
  \resumeSubHeadingListEnd


%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Indian Institute of Information Technology, Kottayam}{Kerala, India}
      {BTech Computer Science, (Artificial Intelligence and Data Science) : 8.3 CGPA}{Nov. 2022 -- Present}
  \resumeSubHeadingListEnd

%-------------------------------------------
\end{document}
